% !TEX root = master_kmatsui.tex
In this paper, we present IllumiConnect, a novel technique for realize a hand gesture operation to enable multi-device interaction.
IllumiConnect uses illuminance meter built into mobile devices such as smartphones and tablet terminal to sense hand gestures performed over between mobile devices.
By recognizing hand gestures using decision tree learning based on  history of illuminance value, we realize a intuitive operation by hand gestures over mobile devices.
We conducted two kind of experiments for evaluating IllumiConnect.
In an evaluation experiment for accuracy of hand gestures recognition, IllumiConnect showed to be able to distinguish each one of hand gestures high accuracy.
And in an evaluation experiment for verifying accuracy of grouping some devices, IllumiConnect showed to be able to group devices almost correct.
We also implemented a application and introduce a specific use case of IllumiConnect.

\begin{comment}
  日本語
  本稿では，私たちはIllumiConnect，複数端末間のインタラクションを可能とするためのハンドジェスチャ操作を実現する新しい技術，を示す．
  IllumiConnectは，モバイル端末の上で行われたジェスチャを認識するために，スマートフォンやタブレット端末などのモバイル端末に内蔵された照度センサを用いる.
  照度値の履歴を基にした決定木学習を用いてハンドジェスチャを認識することで，私たちはモバイル端末上でのハンドジェスチャによる直感的な操作を実現す．
  私たちは，IllumiConnectを評価するために二種類の評価実験を行った．
  ハンドジェスチャ認識精度を検証するための評価実験では，IllumiConnectは高い精度でそれぞれのジェスチャを認識可能であることを示した。
  また，任意デバイスのグルーピング化の精度を検証するための評価実験では，IllumiConnectは，ほとんど正確に端末をグルーピングできることを示した．
  また，私たちは，アプリケーションを作成し, IllumiConnectの具体的な使用例を紹介する．
\end{comment}

%-----------------------
%近年，ほとんどの人がスマートフォンを所持している．
%また，1人の人がスマートフォンやタブレット，スマートウォッチなど複数のモバイル端末を所有している．
%このようにモバイル端末が多くなってきているので，モバイル端末間でのデータ共有やグルーピングなどに対しての需要が高まっている．
%しかし，それらを行うためには，複雑な操作が必要となる．
%例えば，近くにあるデバイスを検出し，送りたいデバイスを選択する．
%そして，そのデバイスと接続できたら，送りたいデータを選択しそのデバイスに送信する．
%そこで，この問題を解消するために直感的な操作によりデータ送信やグルーピングを行う研究がたくさん行われている．
%しかし，これらの操作にも問題はある．
%そこで，本稿では，モバイル端末に内蔵されている照度センサを用いて，複数端末の連携をハンドジェスチャによる直感的な操作により実現するIllumiConnectを作成した．
%IllumiConnectのジェスチャ操作の認識精度の検証と複数のモバイル端末でのグルーピング精度の検証を行うために被験者実験を行った．
%その結果，IllumiConnectはジェスチャ操作を高い精度で認識し、また、ほとんど確実にグルーピングできることがわかった．
